### 2022-11-13 NSF2022/Description/backgroundv3.tex
fixed up graphics

\subsection{Problem formulation}
To formulate the problem, consider a collection of $N_b$-many rigid
bodies $U_i(t) \subset \RR^n$ with boundary $\Gamma_i(t)$. We call these
bodies ``granules''. The granules are immersed in an incompressible,
zero-Reynolds number fluid $\Omega(t) = \RR^n \setminus \cup_{i=1}^{N_b}
U_i(t)$ (Figure~\ref{fig:flow_map}).
Throughout, $\nnu$ refers to unit
normal pointing into $\Omega(t)$ (Figure~\ref{fig:flow_map}).

@@

@@

\begin{wrapfigure}[22]{r}{3.2in}
  \vspace{-15pt}
  \begin{center}
    \begin{tabular}{m{0.9in}m{0.9in}m{0.9in}}                 
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B3.jpg}    \\
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C3.jpg}    \\
      \includegraphics[width=0.85in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A3.jpg} 
  \end{tabular}
  \end{center}
  \vspace{-15pt}
  \caption{\footnotesize \label{fig:self-assembly2}
  Changes in the boundary condition \eqref{eqn:material}
  yield distinct morphologies.
  Each row has the same initial configuration, $W(\phi) = \tfrac{1}{2}\phi^2$.
  (\emph{Top}) Granules with an amphiphilic boundary condition
  results in a bilayer pattern (yellow,
  $\phi = 1$, blue, $\phi = 0$).
  (\emph{Middle}) Granules with $\phi = 2$ (magenta) on one side and $\phi = 1$
  on the other   form multilamellar bilayers.
  (\emph{Bottom}) Bipolar granules with $\phi = \pm 1$ (yellow, green, resp.)
  on poler ends   form a checkerboard pattern.}
\end{wrapfigure}
\subsection{Applications}
Since the framework is scale independent, it can be applied broad
range of nonspecific self-organization phenomena in surface chemistry,
biology and engineering. For one, the
formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
the right behavior expected from amphiphilic self-assembly.
For example, three bodies with amphiphilic label (\S\ref{sec:specificaim1})
spontaneously self-organize to sequester the hydrophobic fluid phase
(Figure~\ref{fig:flow_map}).
Changes in the boundary conditions result in
distint morphologies
(Figure~\ref{fig:self-assembly2})
whose rheology can be further investigate (\S\ref{sec:specificaim3}).

@@

@@

\begin{wrapfigure}[10]{l}{0.46\textwidth}
\includegraphics[width=0.46\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
\caption{\label{fig:JPv_linearshear}Granular vesicles undergo
tank-treading in background shear flow.}
\end{wrapfigure}
Having a non-specific model that replicates physical details
is the crown jewel of applied mathematics.
\emph{Further applications} include
(i) amphiphilic Janus spheres that form diverse suprastructures
\cite{HaBr20,McBr21,Bradley2017},
(ii) pickering emulsions involving
two-phase fluids and dense suspensions \cite{Bradley2016},
(iii) creation and manipulation of small droplets
using amphiphilic microparticles \cite{Ha2022SurfaceEM,Ha2020MinimalSC},
and (iv) tension drivent fabrication of microstructures
~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,Zeng20223DprintedMT,Russell2016EnergyLF}.
\newline

\subsection{Computational method and mathematical properties}
\begin{wrapfigure}[14]{r}{0.475\textwidth}
%\vspace{-10pt}
\includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
\caption{\label{fig:JPv_rupture}Rupture of a granular vesicle under large shear rates.}
\end{wrapfigure}
Computational methods to solve the PDEs~\eqref{eqn:stokes}
and~\eqref{eqn:phase} are challenging to develop because of
the complicated and unbounded domain.
This challenge is compounded when dense
suspensions are considered. Integral equations (IEs) offer an
alternative formulation of the PDEs that only require meshing the
boundary of the granules rather than all of $\Omega(t)$
(Figure~\ref{fig:fem_vs_bie}), and the automatically satisfy far field
conditions. Additional advantages of an discretizations of IE
formulations include high-order, or even spectral, accuracy and
well-conditioned linear system that can be solved iteratively with a
mesh-independent number of Krylov iterations such as the generalized
minimal residual method (GMRES). However, IEs have challenges: nearly
touching granules requires a quadrature rule for nearly-singular
integrals; their discretization results in dense matrices; and they
cannot immediately be applied to non-linear PDEs. The IE community,
including PI Quaife, has developed a variety of tools to address these
numerical challenges, and we discuss in \S~\ref{sec:specificaim2}.

In the absence of external flow, the
system~\eqref{eq:RBT}--\eqref{eqn:stressbalance} has the energy law
\begin{align}
\label{eq:energy_law}
  \frac{d}{dt}E
  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2 \,d\xx,\quad
    E = \gamma \int_{\Omega(t)}
  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
\end{align}
Here $E$ is the energy stored in the phase transitions
and the energy law states that
the granules move to decrease energy,
which is lost due to viscous dissipation.
The derivation of \eqref{eq:energy_law} is interesting
because $E$ depends both on $\phi$
and $\Omega(t)$. It uses the Rayleigh Transport Theorem to write the time
derivative of $E$ as an energy density flux through the boundary
involving the phase stress $T_i$, and a bulk term involving the Euler-Lagrange
derivative of $E$~\cite{Fu2018_SIAM}. The Euler-Lagrange derivative vanishes due
to~\eqref{eqn:phase} and the boundary flux transforms into viscous
dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations. Figure~\ref{fig:coarsening} summarizes the general evolution of $E$ from the self-assembly process to
the collective dynamics of the assembly under external forcing.

\begin{wrapfigure}[17]{l}{4in} 
\includegraphics[width=4in]{figures/Background/coarsening.pdf}
\vspace{-20pt}
\caption{\label{fig:coarsening}
Energy $E$ in equation~(\ref{eq:energy_law}) of a suspension of amphiphilic granules versus time $t$.
Under the moving domain problem
\eqref{eq:RBT}-\eqref{eqn:hydro_stress}
with amphiphilic boundary condition, the granules
self-organize into vesicle bilayers.
External hydrodynamic effects are introduced to study elastic properties the the granules assembly \cite{Fu2018_SIAM,FuQuRyYo22}.
}
\vspace{5pt}
\end{wrapfigure}
In the far field, $\lim_{\xx \to \infty} \phi(\xx) = \phi_0$ and for the
background flow, we require that $\lim_{\xx \to \infty} \uu(\xx) -
\uu_{\infty}(\xx) = \mathbf{0}$, where
the background flow takes the form
%In the case of shear background flow,
%for example,
%\begin{align}
%\label{eqn:shear_BG_flow}
%\uu_{\infty}(\xx) = \dot{\gamma} \xx \cdot \mathbf{e}_y \mathbf{e}_x,
%\end{align}
%where $\dot \gamma$ is the shear rate and $\mathbf{e}_x$, $\mathbf{e}_y$
%are horizontal and vertical basis vectors, respectively.
%Other
%background flows include
shear, extensional, parabolic Poiseuille, and
Taylor-Green flow, for example.
For numerical stability and physical realism, we
include pairwise repulsive forces and torques
in~\eqref{eqn:stressbalance} to prevent the collision between
neighboring granules which introduces a repulsive potential in the energy
law~\eqref{eq:energy_law}. Background flow adds elastic energy to the
granule configurations.
%and is quantified by simulation. We refer to the
%PIs work~\cite{FuQuRyYo22, fu-ryh-qua-you2022, Fu2018_SIAM} for details.

@@

\begin{wrapfigure}[10]{r}{2.1in}
  \centering
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  ({\em left}) requires meshing the entire domain (typically into
  triangles), while a BIE ({\em right}) requires meshing only the
  boundary of the domain.}
\end{wrapfigure}
Regarding mathematical motivation for~\eqref{eq:RBT}--\eqref{eqn:stressbalance},
when equation \eqref{eqn:phase} takes the form of a screened Laplace equation
$-\epsilon^2 \Delta \phi + \phi =0$, for a fixed domain $\Omega$ with
smooth boundary, if the material label $h_i = 1$
everywhere, then $\phi$ has a boundary layer going from $1$ at the
boundary to $0$ in the bulk and one can prove that 
$\lim_{\epsilon \to 0} E = \frac{1}{2}\gamma |\partial \Omega|$.
In other words, 
interfacial energy enters the problem even in the linear case,
\emph{because of the introduction of granule boundaries.}
We are confident
that~\eqref{eq:RBT}--\eqref{eqn:stressbalance} is a correct description
of long-range interactions between granule surfaces.

>>>>

\subsection{Problem formulation}
To formulate the problem, consider a collection of $N_b$-many rigid
bodies $U_i(t) \subset \RR^n$ with boundary $\Gamma_i(t)$. We call these
bodies ``granules''. The granules are immersed in an incompressible,
zero-Reynolds number fluid $\Omega(t) = \RR^n \setminus \cup_{i=1}^{N_b}
U_i(t)$ (Figure~\ref{fig:flow_map}). Throughout, $\nnu$ refers to unit
normal pointing into $\Omega(t)$.

@@

\begin{wrapfigure}[21]{r}{3.2in}
  \vspace{-10pt}
  \begin{center}
    \begin{tabular}{m{0.9in}m{0.9in}m{0.9in}}                 
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B3.jpg}    \\
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C3.jpg}    \\
      \includegraphics[width=0.85in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A3.jpg} 
  \end{tabular}
  \end{center}
  \vspace{-20pt}
  \caption{\footnotesize \label{fig:self-assembly2} Changes in the
  boundary condition \eqref{eqn:material} yield distinct morphologies.
  Each row has the same initial configuration, $W(\phi) =
  \tfrac{1}{2}\phi^2$. (\emph{Top}) Granules with an amphiphilic
  boundary condition results in a bilayer pattern (yellow, $\phi = 1$,
  blue, $\phi = 0$). (\emph{Middle}) Granules with $\phi = 2$ (magenta)
  on one side and $\phi = 1$ on the other form multilamellar bilayers.
  (\emph{Bottom}) Bipolar granules with $\phi = 1$ (yellow) on one side
  and $\phi=-1$ (green) on the other side form a checkerboard pattern.}
\end{wrapfigure}

@@

\subsection{Applications}
Since the framework is scale independent, it can be applied broad range
of nonspecific self-organization phenomena in surface chemistry, biology
and engineering. For one, the
formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
the right behavior expected from amphiphilic self-assembly. For example,
three bodies with amphiphilic label (\S\ref{sec:specificaim1})
spontaneously self-organize to sequester the hydrophobic fluid phase
(Figure~\ref{fig:flow_map}). Changes in the boundary conditions result
in distint morphologies (Figure~\ref{fig:self-assembly2}) whose rheology
can be further investigate (\S\ref{sec:specificaim3}).

@@

\begin{wrapfigure}[10]{l}{0.46\textwidth}
\includegraphics[width=0.46\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
\caption{\label{fig:JPv_linearshear} \footnotesize Granular vesicles
  undergo tank-treading in background shear flow.}
\end{wrapfigure}

@@

\begin{wrapfigure}[14]{r}{0.475\textwidth}
%\vspace{-10pt}
\includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
\caption{\label{fig:JPv_rupture} \footnotesize Rupture of a granular
  vesicle under large shear rates.}
\end{wrapfigure}

Having a non-specific model that replicates physical details
is the crown jewel of applied mathematics.
\emph{Further applications} include
(i) amphiphilic Janus spheres that form diverse suprastructures
\cite{HaBr20,McBr21,Bradley2017},
(ii) pickering emulsions involving
two-phase fluids and dense suspensions \cite{Bradley2016},
(iii) creation and manipulation of small droplets
using amphiphilic microparticles \cite{Ha2022SurfaceEM,Ha2020MinimalSC},
and (iv) tension drivent fabrication of microstructures
~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,Zeng20223DprintedMT,Russell2016EnergyLF}.
\begin{wrapfigure}[8]{l}{2.1in}
  \vspace{-5pt}
  \centering
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  ({\em left}) requires meshing the entire domain (typically into
  triangles), while a BIE ({\em right}) requires meshing only the
  boundary of the domain.}
\end{wrapfigure}

\subsection{Computational method and mathematical properties}
Computational methods to solve the PDEs~\eqref{eqn:stokes}
and~\eqref{eqn:phase} are challenging to develop because of
the complicated and unbounded domain.
This challenge is compounded when dense
suspensions are considered. Integral equations (IEs) offer an
alternative formulation of the PDEs that only require meshing the
boundary of the granules rather than all of $\Omega(t)$
(Figure~\ref{fig:fem_vs_bie}), and the automatically satisfy far field
conditions. Additional advantages of an discretizations of IE
formulations include high-order, or even spectral, accuracy and
well-conditioned linear system that can be solved iteratively with a
mesh-independent number of Krylov iterations such as the generalized
minimal residual method (GMRES). However, IEs have challenges: nearly
touching granules requires a quadrature rule for nearly-singular
integrals; their discretization results in dense matrices; and they
cannot immediately be applied to non-linear PDEs. The IE community,
including PI Quaife, has developed a variety of tools to address these
numerical challenges, and we discuss in \S~\ref{sec:specificaim2}.

In the absence of external flow, the
system~\eqref{eq:RBT}--\eqref{eqn:stressbalance} has the energy law
\begin{align}
\label{eq:energy_law}
  \begin{split}
  \frac{d}{dt}E
  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2 \,d\xx, \\
    E = \gamma \int_{\Omega(t)}
  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
  \end{split}
\end{align}
%\begin{align}
%\label{eq:energy_law}
%  \frac{d}{dt}E
%  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
%  \uu^T|^2 \,d\xx,\quad
%    E = \gamma \int_{\Omega(t)}
%  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
%\end{align}
Here $E$ is the energy stored in the phase transitions
and the energy law states that
the granules move to decrease energy,
which is lost due to viscous dissipation.
The derivation of \eqref{eq:energy_law} is interesting
because $E$ depends both on $\phi$
and $\Omega(t)$. It uses the Rayleigh Transport Theorem to write the time
derivative of $E$ as an energy density flux through the boundary
involving the phase stress $T_i$, and a bulk term involving the Euler-Lagrange
derivative of $E$~\cite{Fu2018_SIAM}. The Euler-Lagrange derivative vanishes due
to~\eqref{eqn:phase} and the boundary flux transforms into viscous
dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations. Figure~\ref{fig:coarsening} summarizes the general evolution of $E$ from the self-assembly process to
the collective dynamics of the assembly under external forcing.
\begin{wrapfigure}[16]{r}{4in} 
  \includegraphics[width=4in]{figures/Background/coarsening.pdf}
  \vspace{-20pt}
  \caption{\label{fig:coarsening} \footnotesize Energy $E$ in
  equation~(\ref{eq:energy_law}) of a suspension of amphiphilic granules
  versus time $t$. Under the moving domain problem
  \eqref{eq:RBT}--\eqref{eqn:hydro_stress} with amphiphilic boundary
  condition, the granules self-organize into vesicle bilayers. External
  hydrodynamic effects are introduced to study elastic properties the
  the granules assembly~\cite{Fu2018_SIAM,FuQuRyYo22}.}
  \vspace{5pt}
\end{wrapfigure}

In the far field, $\lim_{\xx \to \infty} \phi(\xx) = \phi_0$ and for the
background flow, we require that $\lim_{\xx \to \infty} \uu(\xx) -
\uu_{\infty}(\xx) = \mathbf{0}$, where
the background flow takes the form
%In the case of shear background flow,
%for example,
%\begin{align}
%\label{eqn:shear_BG_flow}
%\uu_{\infty}(\xx) = \dot{\gamma} \xx \cdot \mathbf{e}_y \mathbf{e}_x,
%\end{align}
%where $\dot \gamma$ is the shear rate and $\mathbf{e}_x$, $\mathbf{e}_y$
%are horizontal and vertical basis vectors, respectively.
%Other
%background flows include
shear, extensional, parabolic Poiseuille, and
Taylor-Green flow, for example.
For numerical stability and physical realism, we
include pairwise repulsive forces and torques
in~\eqref{eqn:stressbalance} to prevent the collision between
neighboring granules which introduces a repulsive potential in the energy
law~\eqref{eq:energy_law}. Background flow adds elastic energy to the
granule configurations.
%and is quantified by simulation. We refer to the
%PIs work~\cite{FuQuRyYo22, fu-ryh-qua-you2022, Fu2018_SIAM} for details.

@@

Regarding mathematical motivation for~\eqref{eq:RBT}--\eqref{eqn:stressbalance},
when equation \eqref{eqn:phase} takes the form of a screened Laplace equation
$-\epsilon^2 \Delta \phi + \phi =0$, for a fixed domain $\Omega$ with
smooth boundary, if the material label $h_i = 1$
everywhere, then $\phi$ has a boundary layer going from $1$ at the
boundary to $0$ in the bulk and one can prove that 
$\lim_{\epsilon \to 0} E = \frac{1}{2}\gamma |\partial \Omega|$.
In other words, 
interfacial energy enters the problem even in the linear case,
\emph{because of the introduction of granule boundaries.}
We are confident
that~\eqref{eq:RBT}--\eqref{eqn:stressbalance} is a correct description
of long-range interactions between granule surfaces.

### 2022-11-13 NSF2022/Description/specificaim2.tex
fixed up graphics

In experiments, it is known that interactions between bounding walls and
granules cannot be ignored~\cite{qua-gan-you2021,
KaouiHartingMisbah2011_PRE, her-sto-gra2005}. Therefore, the necessary
modification to the code will be implemented so that confinement can be
considered. This modification requires introducing an additional layer
potential on the bounding walls, and elements of this modification have
already been incorporated (Figure~\ref{fig:stenosis}). However, to
consider rheological properties of the suspensions, a periodic domain,
such as a Couette device, will be considered. Such multiply-connected
domains require additional modifications to the IE formulation. PI
Quaife has considered suspensions with confinement for several projects
including dynamic suspensions~\cite{qua-bir2014, bys-sha-qua2020} and
porous media~\cite{chi-moo-qua2020, dea-qua-bir-jua2018,
moo-che-chi-qua2022, qua-gan-you2021}.

@@

\begin{wrapfigure}[]{r}{2.1in}
  \centering
  \input{figures/near_sing.tikz}
  \caption{\label{fig:interpquad} \footnotesize An interpolation-based
  quadrature method that works in two and three dimensions. The
  spectrally-accurate trapezoid rule is used in points in
  $\mathtt{Far}(\Gamma_i)$, while one dimensional interpolant is used
  for points in $\mathtt{Near}(\Gamma_i)$. $h$ is the arclength
  spacing.}
\end{wrapfigure}

Since we are interested in round (2D) and spherical (3D) granules, we
will exploit the fact that integrals can be computed with spectral
accuracy by transforming the integrals to to a Fourier (2D) or spherical
harmonic (3D) basis. This technique can be used to evaluate layer
potentials for both Stokes~\cite{cor-vee2018} and the screened Laplace
equation~\cite{koh-cor-che-vee2021}. However, this quadrature is not
appropriate or other shapes, and an alternative approach is necessary.
The Barycentric-type formulae for Cauchy integrals results in a
uniformly bounded quadrature error, but the method is described only for
the two-dimensional Laplace and Stokes equations. PI Quaife recently
showed that these quadrature methods can be extended to other
two-dimensional PDEs~\cite{che-lin-her-qua2022}. The method uses
singularity subtraction write the fundamental solution of the PDE as a
sum of two terms: a logarithmic function and a continuously
differentiable function. Then the Barycentric-type formulae can be
applied to the logarithmic function, and the standard trapezoid
rule~\cite{tre-wei2014} can be applied to the other function. These
singularity subtraction methods can also accurately compute derivatives
of layer potentials~\cite{car2021, car2020, car-kha-kim2018} which is
required, for example, when computing the water-order
stress~\eqref{eqn:stressbalance}. Singularity subtraction methods can
also be applied in three dimensions, but not combined with
Barycentric-type formulae. Alternatively, smoothed variations of the
fundamental solution can be used to address nearly-singular
integrals~\cite{beale1, cor2001, tlu-bea2019}. Alternatively, efficient
quadrature methods can be applied directly to accurately compute
singular and near-singular integrals~\cite{khayat_2005,
gimbutas2013sisc}.

@@

\begin{wrapfigure}[27]{l}{1.8in}
  \vspace{-8pt}
  \centering
  \input{figures/doublewell.tikz} 
  \caption{\label{fig:CA} \footnotesize (a) A double-well potential. (b)
  The solution of the one-dimensional phase
  transition~\eqref{eqn:phase}. (c) The convergence of exact and inexact
  Newton's methods.}
\end{wrapfigure}
While the inclusion of high-order quadrature and fast methods is
necessary to simulate dense suspensions, an additional required
computational tool is a collision-aware adaptive time stepping method.
The order parameter results in the granules attracting one another and
this leads to physical contact in finite time. Our current
implementation uses a repulsive Lennard-Jones force, but this introduces
stiffness, thereby requiring small time steps, and this can be a
bottleneck when simulating dense suspensions. Therefore, we will develop
a high-order collision-avoiding adaptive time stepping method. This
method will avoid collisions with by using the minimal separation
distance to impose a non-overlapping constraint. This results in a
linear complementarity problem that can be solve efficiently with a
projected gradient descent method~\cite{Yan2019}. High-order time
adaptivity will be based on PI Quaife's previous work on
suspensions~\cite{qua-bir2016}, and this method has proven to be a
robust method to simulate dense suspensions~\cite{qua-vee-you2019,
kab-qua-bir2017, qua-gan-you2021}. Following this previous work, the
proposed work will use a spectral deferred correction method since it
iteratively applies a low-order, single-step method to achieve
high-order accuracy. At each time step, we will compute the total force
and torque of the system which is computationally cheap and physically
zero, and therefore provides an estimate of the local truncation error.
PI Quaife's experience is that error estimates based on physical
constraints, such as force- and torque-free conditions, appropriately
determine adaptive time step sizes so that the dynamics are resolved
without the computational expense of techniques such as embedded
Runge-Kutta, step-doubling, and Richardson extrapolation.

>>>>

In experiments, it is known that interactions between bounding walls and
granules cannot be ignored~\cite{qua-gan-you2021,
KaouiHartingMisbah2011_PRE, her-sto-gra2005}. Therefore, the necessary
modification to the code will be implemented so that confinement can be
considered. This modification requires introducing an additional layer
potential on the bounding walls, and elements of this modification have
already been incorporated (Figure~\ref{fig:stenosis}). However, to
consider rheological properties of the suspensions, a periodic domain,
such as a Couette device, will be considered. Such multiply-connected
domains require additional modifications to the IE formulation. PI
Quaife has considered suspensions with confinement for several projects
including dynamic suspensions~\cite{qua-bir2014, bys-sha-qua2020} and
porous media~\cite{chi-moo-qua2020, dea-qua-bir-jua2018,
moo-che-chi-qua2022, qua-gan-you2021}.
\begin{wrapfigure}[16]{r}{2.1in}
  \vspace{-8pt}
  \centering
  \input{figures/near_sing.tikz}
  \vspace{-15pt}
  \caption{\label{fig:interpquad} \footnotesize An interpolation-based
  quadrature method that works in two and three dimensions. The
  spectrally-accurate trapezoid rule is used in points in
  $\mathtt{Far}(\Gamma_i)$, while one dimensional interpolant is used
  for points in $\mathtt{Near}(\Gamma_i)$. $h$ is the arclength
  spacing.}
\end{wrapfigure}

@@

Since we are interested in round (2D) and spherical (3D) granules, we
will exploit the fact that integrals can be computed with spectral
accuracy by transforming the integrals to to a Fourier (2D) or spherical
harmonic (3D) basis. This technique can be used to evaluate layer
potentials for both Stokes~\cite{cor-vee2018} and the screened Laplace
equation~\cite{koh-cor-che-vee2021}. However, this quadrature is not
appropriate or other shapes, and an alternative approach is necessary.
The Barycentric-type formulae for Cauchy integrals results in a
uniformly bounded quadrature error, but the method is described only for
the two-dimensional Laplace and Stokes equations. PI Quaife recently
showed that these quadrature methods can be extended to other
two-dimensional PDEs~\cite{che-lin-her-qua2022}. The method uses
singularity subtraction write the fundamental solution of the PDE as a
sum of two terms: a logarithmic function and a continuously
differentiable function. Then the Barycentric-type formulae can be
applied to the logarithmic function, and the standard trapezoid
rule~\cite{tre-wei2014} can be applied to the other function. These
singularity subtraction methods can also accurately compute derivatives
of layer potentials~\cite{car2021, car2020, car-kha-kim2018} which is
required, for example, when computing the water-order
stress~\eqref{eqn:stressbalance}. Singularity subtraction methods can
also be applied in three dimensions, but not combined with
Barycentric-type formulae. Alternatively, smoothed variations of the
fundamental solution can be used to address nearly-singular
integrals~\cite{beale1, cor2001, tlu-bea2019}. Alternatively, efficient
quadrature methods can be applied directly to accurately compute
singular and near-singular integrals~\cite{khayat_2005,
gimbutas2013sisc}.
\begin{wrapfigure}[27]{l}{1.8in}
  \vspace{-8pt}
  \centering
  \input{figures/doublewell.tikz} 
  \vspace{-10pt}
  \caption{\label{fig:CA} \footnotesize (a) A double-well potential. (b)
  The solution of the one-dimensional phase
  transition~\eqref{eqn:phase}. (c) The convergence of exact and inexact
  Newton's methods.}
\end{wrapfigure}

@@

While the inclusion of high-order quadrature and fast methods is
necessary to simulate dense suspensions, an additional required
computational tool is a collision-aware adaptive time stepping method.
The order parameter results in the granules attracting one another and
this leads to physical contact in finite time. Our current
implementation uses a repulsive Lennard-Jones force, but this introduces
stiffness, thereby requiring small time steps, and this can be a
bottleneck when simulating dense suspensions. Therefore, we will develop
a high-order collision-avoiding adaptive time stepping method. This
method will avoid collisions with by using the minimal separation
distance to impose a non-overlapping constraint. This results in a
linear complementarity problem that can be solve efficiently with a
projected gradient descent method~\cite{Yan2019}. High-order time
adaptivity will be based on PI Quaife's previous work on
suspensions~\cite{qua-bir2016}, and this method has proven to be a
robust method to simulate dense suspensions~\cite{qua-vee-you2019,
kab-qua-bir2017, qua-gan-you2021}. Following this previous work, the
proposed work will use a spectral deferred correction method since it
iteratively applies a low-order, single-step method to achieve
high-order accuracy. At each time step, we will compute the total force
and torque of the system which is computationally cheap and physically
zero, and therefore provides an estimate of the local truncation error.
PI Quaife's experience is that error estimates based on physical
constraints, such as force- and torque-free conditions, appropriately
determine adaptive time step sizes so that the dynamics are resolved
without the computational expense of techniques such as embedded
Runge-Kutta, step-doubling, and Richardson extrapolation.
